How did the introduction of Stemmed Points affect Mobility and Site Occupation during the Late Pleistocene in Korea?

### 2021-01-15 analysis/paper/paper.Rmd
adjust legand for SPD and knit rmd file

```{r}	
quietly <- function(x) {	
  sink(tempfile())	
  on.exit(sink())	
  invisible(force(suppressMessages(x)))	
}	
```
# Introduction {-}

@@

```{r spd-model, fig.cap="Summed probability distribution of 108 radiocarbon dates. The black solid line represents actual radiocarbon ages. The grey shaded region shows the critical envelope that encompasses the 95% confidence interval for the null models. The red and blue vertical bands highlight the portions of the SPD where positive and negative deviations are detected. We applied logistic, exponential and linear to AIC along with the logistical growth model (fit) to evaluate each model [@riris2019widespread]. We excluded the uniform model because it has no fitted curve or surface to evaluate. The best fit model has the lowest AIC score. In this case, the linear model is the best fit, with the next-best fit (exponential) having a higher AIC score by a minor margin at -48.6.", cache=TRUE, cache.extra=tools::md5sum(here::here("analysis/paper/008-summed-probability-distributions.R"))}
quietly(source(here::here("analysis/paper/008-summed-probability-distributions.R")))
knitr::include_graphics(here::here("analysis/figures/008-summed-probability-distribution-models.png"))
```

@@

>>>>

```{r}	
quietly <- function(x) {	
  sink(tempfile())	
  on.exit(sink())	
  invisible(force(suppressMessages(x)))	
}	
```

# Keywords {-}
Human Behavioural Ecology, Stemmed points, Mobility, Site occupation, Landscape use, Summed Probability Distribution, Pleistocene, Korean Late Paleolithic

# Introduction {-}

@@

```{r spd-model, fig.cap="Summed probability distribution of 108 radiocarbon dates. The black solid line represents actual radiocarbon ages. The grey shaded region shows the Monte Carlo envelope that encompasses the 95% confidence interval for the null models. The red and blue vertical bands highlight the portions of the SPD where positive and negative deviations are detected. We applied logistic, exponential and linear to AIC along with the logistical growth model (fit) to evaluate each model [@riris2019widespread]. We excluded the uniform model because it has no fitted curve or surface to evaluate. The best fit model has the lowest AIC score. In this case, the linear model is the best fit, with the next-best fit (exponential) having a higher AIC score by a minor margin at -48.6.", cache=TRUE, cache.extra=tools::md5sum(here::here("analysis/paper/008-summed-probability-distributions.R"))}
quietly(source(here::here("analysis/paper/008-summed-probability-distributions.R")))
knitr::include_graphics(here::here("analysis/figures/008-summed-probability-distribution-models.png"))
```

@@

# CRediT authorship contribution statement {-}
Gayoung Park: Conceptualization, Data curation, Methodology, Software, Validation, Formal analysis, Resources, Writing - original draft, Visualization, Project administration, Funding acquisition.

Ben Marwick: Methodology, Formal analysis, Investigation, Software, Validation, Visualization, Supervision, Project administration, Funding acquisition.

# Funding source {-}
This work was supported by Quaternary Research Center funding, and travel grants from the Department of Anthropology and Center for Statistics and the Social Sciences at University of Washington.
